A Survey of Scientific Workflow Management Systems

### 2014-05-09 paper.tex
bib fixes

% == ENACTOR SCALABILITY AND OPTIMIZATION ==
\section{Enactor Scalability and Optimization} \label{sec:scal}
%We have results comparing \MOTEUR and Taverna performance!
%For Pegasus: Scaling up workflow based applications.
A simple definition of scalability in the context of SWE is that the
performance of the workflow engine increases linearly with the increasing
number of similar tasks. Depending upon the lag or increase in the linearity we
say a workflow enactor scales up or down.  In this section, we focus on
the scalability aspects of the workflow runtime. We do not consider the
specific scalability issues related to a distributed infrastructure such as
network latencies and protocol related overheads. However, there have been efforts to
thwart such issues at the workflow level by combining workflow enactment
techniques with those of distributed computing.  One such example is the
map/reduce framework \cite{mapreduce}.  Recently, the map/reduce framework,
that aims at performing distributed processing on large datasets, has gained a
significant popularity in workflow community. It is based on the master/worker
metaphor of distributed processing.  It employs the commonly used \textit{map}
and \textit{reduce} functions from the functional programming languages. The
map function chops a large chunk of data into smaller pieces and distributes it
to \textit{workers} which in turn can also chop it to further smaller datasets
forming a tree-like hierarchy. The worker process the data and return the
results back to their parents. The reduce step collects the results from the
workers and combines them to obtain the final result. One of the main reason
for the popularity of the map/reduce framework for workflows is the recent
attention to collections based datasets and processing. There exists
implementations of the map/reduce framework written in different languages with
enhancements and support services such as a sophisticated query service. Hadoop
(\textit{http://hadoop.apache.org/}) is one such implementation which has
already been interfaced by the Kepler SWE~\cite{wang-crawl-etal:2009}.

@@

Taverna version 2.x introduced new measures in order to be able to submit a
large number of jobs simultaneously. It is able to dispatch large number of
concurrent instances of processors. An ability to implement superpipelined
\cite{hwang:1992} execution of workflow tasks leads to a maximum expression of
parallelism.

@@

The Pegasus workflow manager introduced subworkflows because of scalability
issues at the local host for a large number of nodes in a DAG. A hierarchical
representation helps it scale at the local planning level as well as at the
execution level on distributed resources.

Static planners in Pegasus translate a workflow graph into a location specific
DAGMan input file, adding stages for data staging, intersite transfer and data
registration. These planners can reduce processing of tasks for files that
already exist, select sites for jobs, and cluster jobs based on various
criteria. Pegasus performs graph transformation with the knowledge of the whole
workflow graph.

@@

\begin{table}[ht!]
\begin{center}
% use packages: array
\begin{tabular}{|l|l|l|l|l|l|l|}
\hline
\textbf{SWE} / & \multicolumn{3}{c|}{\textbf{Parallelism}} & \multicolumn{3}{c|}{\textbf{Optimization}}\\
\cline{2-7}
\textbf{Language} & \textbf{data} & \textbf{workflow} & \textbf{pipeline} & \textbf{static} & \textbf{runtime} & \textbf{other}\\ \hline
Taverna/Scufl2 & \checkmark & \checkmark & \checkmark & -- & \checkmark & -- \\\hline
+/BPEL &foreach & \checkmark & -- &-- &\checkmark &-- \\\hline
Triana/- & \checkmark & \checkmark & \checkmark & -- & \checkmark &--\\\hline
MOTEUR/Scufl & \checkmark & \checkmark & \checkmark &-- &\checkmark &-- \\\hline
Kepler/MoML & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark &--\\\hline
GridNexus/GXPL & -- & \checkmark & -- &-- &\checkmark &-- \\\hline
Swift/SwiftScript & \checkmark & \checkmark & \checkmark & \checkmark &\checkmark &-- \\\hline
Askalon/AGWL &--& \checkmark & -- & \checkmark & \checkmark & -- \\\hline
P-GRADE/- &\checkmark &\checkmark &\checkmark &--&--&--\\\hline
Pegasus/DAX &\checkmark &\checkmark &\checkmark &\checkmark &\checkmark &AI-based techniques \\\hline
Galaxy/- &-- &-- &\checkmark &-- &-- &-- \\\hline
MOTEUR2/Gwendia~ & \checkmark &\checkmark & \checkmark &-- &\checkmark &-- \\\hline
\end{tabular}
%\caption{A summary of SWEs Scalability and optimization Mechanisms}
\label{tbl:scalability}
\end{center}
\end{table}

>>>>

% == SYSTEM SCALABILITY AND OPTIMIZATION ==
\section{Scalability and Optimization} \label{sec:scal}
%We have results comparing \MOTEUR and Taverna performance!
%For Pegasus: Scaling up workflow based applications.
A simple definition of scalability in the context of SWE is that the
performance of the workflow engine increases linearly with the increasing
number of similar tasks. Depending upon the lag or increase in the linearity we
say a workflow enactor scales up or down.  In this section, we focus on
the scalability aspects of the workflow runtime. We do not consider the
specific scalability issues related to a distributed infrastructure such as
network latencies and protocol related overheads. However, there have been efforts to
thwart such issues at the workflow level by combining workflow enactment
techniques with those of distributed computing.  One such example is the
map/reduce framework \cite{mapreduce}.  Recently, the map/reduce framework,
that aims at performing distributed processing on large datasets, has gained a
significant popularity in workflow community. It is based on the master/worker
metaphor of distributed processing.  It employs the commonly used \textit{map}
and \textit{reduce} functions from the functional programming languages. The
map function chops a large chunk of data into smaller pieces and distributes it
to \textit{workers} which in turn can also chop it to further smaller datasets
forming a tree-like hierarchy. The worker process the data and return the
results back to their parents. The reduce step collects the results from the
workers and combines them to obtain the final result. One of the main reason
for the popularity of the map/reduce framework for workflows is the recent
attention to collections based datasets and processing. There exists
implementations of the map/reduce framework written in different languages with
enhancements and support services such as a sophisticated query service. Hadoop
(\textit{http://hadoop.apache.org/}) is one such implementation which has
already been interfaced by the Kepler SWE~\cite{wang-crawl-etal:2009}.

@@

Taverna version 2.x introduced new measures in order to be able to submit a
large number of jobs simultaneously. It is able to dispatch large number of
concurrent instances of processors. An ability to implement
superpipelined~\cite{hwang:1992} execution of workflow tasks leads to a maximum
expression of parallelism~\cite{pipeline}.

@@

The Pegasus workflow manager introduced subworkflows because of scalability
issues at the localhost for a large number of nodes in a DAG. A hierarchical
representation helps it scale at the local planning level as well as at the
execution level on distributed resources.

Static planners in Pegasus translate a workflow graph into a location specific
DAGMan input file, adding stages for data staging, intersite transfer and data
registration. These planners can reduce processing of tasks for files that
already exist, select sites for jobs, and cluster jobs based on various
criteria. Pegasus performs graph transformation with the knowledge of the whole
workflow graph. A similar strategy is grouping tasks by application-level
wrappers written in higher-level programming languages such as bash or Python.

@@

\begin{table}[ht!]
%TODO: Caption is not printing well, fix
%\caption{A summary of SWEs Scalability and optimization Mechanisms}
\begin{center}
% use packages: array
\begin{tabular}{|l|l|l|l|l|l|}
\hline
\textbf{SWE} / & \multicolumn{3}{c|}{\textbf{Parallelism}} & \multicolumn{2}{c|}{\textbf{Optimization}}\\
\cline{2-6}
\textbf{Language} & \textbf{data} & \textbf{task} & \textbf{pipeline} & \textbf{static} & \textbf{runtime}\\
\hline
Taverna/Scufl2 & \checkmark & \checkmark & \checkmark & -- & \checkmark \\
\hline
Triana/- & \checkmark & \checkmark & \checkmark & -- & \checkmark \\
\hline
MOTEUR/Scufl & \checkmark & \checkmark & \checkmark &-- &\checkmark \\
\hline
Kepler/MoML & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark \\
\hline
GridNexus/GXPL & -- & \checkmark & -- &-- &\checkmark \\
\hline
Swift/SwiftScript & \checkmark & \checkmark & \checkmark & \checkmark &\checkmark \\
\hline
Askalon/AGWL &--& \checkmark & -- & \checkmark & \checkmark \\
\hline
P-GRADE/- &\checkmark &\checkmark &\checkmark &--&--\\
\hline
Pegasus/DAX &\checkmark &\checkmark &\checkmark &\checkmark &\checkmark \\
\hline
Galaxy/- &-- &-- &\checkmark &-- &-- \\
\hline
MOTEUR2/Gwendia~ & \checkmark &\checkmark & \checkmark &-- &\checkmark \\
\hline
\end{tabular}
\label{tbl:scalability}
\end{center}
\end{table}
